# Walkthrough
## Installing packages
This section is for going over how to download packages and load them into the environment. Packages can be downloaded through CRAN, Bioconductor, or GitHub. 

For installing through CRAN: 
```{r}
install.packages("dplyr") #Downloads packages from CRAN and requires quotations 
library(dplyr) #Loads package into the environment and does not use quotations
sessionInfo() #Shows you what packes are loaded 
```

Remember that you can add a ? in front of functions to bring up help pages to better understand how to use them. 

Other functions that may be useful: 
```{r}
remove.packages("dplyr") #Removes package by uninstalling from computer 
installed.packages() #Shows packages installed but not yet loaded 
sessionInfo() #Tells you which packes are loaded into the instance 
citation(dplyr) #Gives citation information for packages 
#| eval: FALSE
```

For installing through bioconductor: 
```{r}
install.packages("BiocManager") #CRAN package that allows for downloading from Bioconductor
library(BiocManager)
install("PeacoQC") #BiocManager function that installs Bioconductor packages
library(PeacoQC)
sessionInfo()
```

For installing through GitHub: 
```{r}
install.packages("remotes") #CRAN package allowing for downloads from GitHub
library(remotes)
install_github("hally166/flowSpectrum") #remotes function that installs GitHub packages; hally166 is user and flowSpectrum is package name 
library(flowSpectrum)
sessionInfo()
```

Downloading packages needed for the course: 
```{r}
install.packages("purrr") #CRAN
install("flowCore") #Bioconductor 
install("flowWorkspace") #Bioconductor 
#package(s) not installed when version(s) same as or greater than current; use `force = TRUE` to re-install:
install.packages("stringr") #CRAN
install.packages("ggplot2") #CRAN
install("ggcyto") #Bioconductor
install.packages("tidyr") #CRAN
install("openCyto") #Bioconductor
install("FlowSOM") #Bioconductor 
install.packages("xml2") #CRAN
install_github("saeyslab/CytoNorm") #GitHub
install.packages("lubridate") #CRAN
install.packages("httr2") #CRAN
install("flowGate") #Bioconductor 
install.packages("devtools") #CRAN
install.packages("plotly") #CRAN
install_github("biosurf/cyCombine") #GitHub
install("CytoML") #Bioconductor
install.packages("Rtsne") #CRAN
install.packages("uwot") #CRAN
```


